---
title: "viz_and_eda"
output: github_document
---

This is the project/repo for viz_and_eda
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggridges)
```
## creating a data frame
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(c("USW00094728", "USC00519397", "USS0023B17S"),
                      var = c("PRCP", "TMIN", "TMAX"), 
                      date_min = "2017-01-01",
                      date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY", 
                      USC00519397 = "Waikiki_HA",
                      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

## create a ggplot

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point()
```

alternate way of making this plot

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point()
```
saving initial plots- not printing anything, just saving the code
```{r}
scatterplot = 
  weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point()

scatterplot
```
adding color- alpha blending sets transparency of the plots

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = .5) +
  geom_smooth(se = FALSE)
```
turning the 1 panel plot to a 3 panel plot- called facets
```{r}
ggplot(weather_df, aes(x = tmin, y = tmax, color = name)) + 
  geom_point(alpha = .5) +
  geom_smooth(se = FALSE) + 
  facet_grid(. ~ name)
```
```{r}
weather_df %>%
  ggplot(aes(x = date, y = tmax, color = name)) +
  geom_point() +
  geom_smooth(se = FALSE) 
```
## some extra stuff
```{r}
ggplot(weather_df, aes(x = date, y = tmax, color = name)) + 
  geom_smooth(se = FALSE) 
```
install.packages ("hexbin")
2d density
```{r}
ggplot(weather_df, aes(x = tmax, y = tmin)) + 
  geom_hex()
```
## more kinds of plots
```{r}
ggplot(weather_df, aes(x = tmax, fill = name)) + 
  geom_histogram() +
  facet_grid(~name)
```
```{r}
weather_df %>%
  ggplot(aes(x = name, y = tmax)) +
  geom_boxplot()
```
## ridge plots
```{r}
ggplot(weather_df, aes(x = tmax, y = name)) + 
  geom_density_ridges(scale = .85)
```




